The Two-Column Specht Module of the Hecke Algebra of $S_n$

### 2019-07-12 tex/Crossingless.tex
Cleaned up action macro, changed ifthenelse to ifnum
Split matching macros into NatMacros and MilesMacros for workaround
yeet
Initial proof for fibonacci representation

\documentclass{amsart}   
\usepackage{RepStyle}

\usepackage{CJKutf8}

\begin{document}

@@

\section{Introduction}
Let $S_{2n}$ be the symmetric group on $2n$ indices, let $\SH = \SH_{k,q}(S_{2n})$ be the corresponding Hecke algebra with parameter $q$, and let $S = \cbr{T_1,\dots,T_{n-1}}$ be the simple transpositions generating $\SH$.
Let $\brk{k}_q = 1 + q + \dots + q^{k-1}$ be the $q$-number of $K$. 
Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
Either $q = 1$ and $e$ is the characteristic of $k$, or $q \neq 1$ and $q$ is a primitive $e$th root of unity.

Let $V := S^{(2,\dots,2)}$ be the Specht module corresponding to the young diagram with rows of length 2.
The purpose of this writing is to characterize this representation via an isomorphism with another representation of $\SH$.
\begin{definition}
  A \emph{crossingless matching} on $2n$ indices is a partition of $\cbr{1,\dots,2n}$ into parts of size $2$ such that no two parts ``cross'', i.e. there are no parts $(a,a')$ and $(b,b')$ such that $a < b < a' < b'$.
  Then, define $W_{2n}$ to be the $\CC$-vector space with basis the set of crossingless matchings on 2n indices.

@@

\newpage
\section{Irreducibility} 
We can now begin by proving that $\Res_{\SH_{k,p}(S_{2n - 1})}^{\SH_{k,p}(S_{2n})} W$ is irreducible;
in partuclar, this implies that $W$ itself is irreducible, as an $\SH$-subrepresentation is a $\SH_{k,p}(S_{2n - 1})$-subrepresentation.
\begin{proposition}
  Set $\SH' := \SH_{k,p}(S_{2n - 2}) \subset \SH$.
  Then, $\Res_{\SH'}^{\SH} W$ is irreducible if $e \geq n + 1$.
\end{proposition}
\begin{proof}
  We will prove the equivalent condition that each vector in $w \in W$ is \emph{cyclic}, i.e. $\SH' w = W$.

>>>>

\documentclass{amsart}   
\usepackage{RepStyle} 
\usepackage{NatMacros} %********REPLACE WITH MilesMacros TO KILL RELIANCE ON \ifnum AND HAVE INCOMPLETE OUTPUT***********bleh
\begin{document}

@@

\section{Introduction}
Let $S_{2n}$ be the symmetric group on $2n$ indices, let $\SH = \SH_{k,q}(S_{2n})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k$, and let $\cbr{T_i}$ be the simple transpositions generating $\SH$.
Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of $m$. 
Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
Either $q = 1$ and $e$ is the characteristic of $k$, or $q \neq 1$ and $q$ is a primitive $e$th root of unity.

Let $V := S^{(2,\dots,2)}$ be the Specht module corresponding to the young diagram with rows of length 2.
The purpose of this writing is to characterize this representation via an isomorphism with another representation of $\SH$.
\begin{definition}
  A \emph{crossingless matching} on $2n$ indices is a partition of $\cbr{1,\dots,2n}$ into parts of size $2$ such that no two parts ``cross'', i.e. there are no parts $(a,a')$ and $(b,b')$ such that $a < b < a' < b'$.
  We will call these arcs.
  Then, define $W_{2n}$ to be the $k$-vector space with basis the set of crossingless matchings on 2n indices.

@@

\newpage
\section{Irreducibility} 
We can now begin by proving that $\Res_{\SH_{k,p}(S_{2n - 1})}^{\SH_{k,p}(S_{2n})} W$ is irreducible;
in partuclar, this implies that $W$ itself is irreducible, as an $\SH$-subrepresentation is a $\SH_{k,p}(S_{2n - 1})$-subrepresentation.
\begin{proposition}
  Set $\SH' := \SH_{k,p}(S_{2n - 2}) \subset \SH$.
  Then, $\Res_{\SH'}^{\SH} W$ is irreducible if $e > n + 1$.
\end{proposition}
\begin{proof}
  We will prove the equivalent condition that each vector in $w \in W$ is \emph{cyclic}, i.e. $\SH' w = W$.
